---
title: "Occupational Prestige: A Reproducible Report"
author: "Julio"
date: today
abstract: |
  This report examines the determinants of occupational prestige using the Prestige dataset (Duncan, 1961), which covers 102 Canadian occupations. We analyse how income, education, gender composition, and occupational type predict prestige scores through descriptive statistics, visualizations, and OLS regression models. Results show that both income and education are strong positive predictors, with the full model explaining approximately 80% of the variance in prestige. The report is fully reproducible and rendered with Quarto.
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    documentclass: article
    papersize: a4
    fontsize: 12pt
    geometry: margin=2.5cm
    colorlinks: true
execute:
  echo: false
  warning: false
  message: false
bibliography: "presentations/bigsss/bib/phd-tesis.bib"
---

```{r}
#| label: setup
#| include: false

if (!requireNamespace("pacman", quietly = TRUE))
  install.packages("pacman", repos = "https://cloud.r-project.org")

pacman::p_load(
  here,
  car,
  dplyr,
  ggplot2,
  vtable,
  kableExtra,
  broom,
  texreg,
  scales
)
```

```{r}
#| label: prep-data
#| include: false

# Load raw data
data(Prestige)
data_orig <- Prestige

# Recode variables
dfstudy1 <- data_orig %>%
  mutate(
    prestige_cont  = prestige,
    income_cont    = income,
    education_cont = education,
    women_pct      = women,
    income_cat = car::recode(income,
      "1000:8000 = 'Low'; 8001:12000 = 'Mid'; else = 'High'"),
    education_level = car::recode(education,
      "lo:10.09 = 'Low'; 10.1:13 = 'Mid'; 13.1:hi = 'High'"),
    prestige_tier = car::recode(prestige,
      "0:30.5 = 'Low'; 30.6:60 = 'Mid'; 60.1:100 = 'High'"),
    blue_collar  = car::recode(type, "'bc'   = 1; else = 0"),
    professional = car::recode(type, "'prof' = 1; else = 0"),
    high_women   = car::recode(women, "50:100 = 1; else = 0")
  ) %>%
  as.data.frame()

# Save processed data
dir.create(here("input/data/proc"), recursive = TRUE, showWarnings = FALSE)
dir.create(here("output/images"),   recursive = TRUE, showWarnings = FALSE)
dir.create(here("output/tables"),   recursive = TRUE, showWarnings = FALSE)
save(dfstudy1, file = here("input/data/proc/dfstudy1.RData"))

# Prepare regression data frame
df_reg <- dfstudy1 %>%
  mutate(
    income_cat      = factor(income_cat,      levels = c("Low", "Mid", "High")),
    education_level = factor(education_level, levels = c("Low", "Mid", "High")),
    high_women      = factor(high_women,  levels = c(0, 1), labels = c("No", "Yes")),
    blue_collar     = factor(blue_collar, levels = c(0, 1), labels = c("No", "Yes"))
  )

# Fit regression models
model_1 <- lm(prestige_cont ~ income_cont + education_cont, data = df_reg)
model_2 <- lm(prestige_cont ~ income_cont + education_cont + women_pct + blue_collar, data = df_reg)
model_3 <- lm(prestige_cont ~ income_cat + education_level, data = df_reg)
model_4 <- lm(prestige_cont ~ income_cat + education_level + high_women + blue_collar, data = df_reg)
```

## Introduction

This report analyses occupational prestige scores from the `Prestige` dataset (Duncan, 1961; `car` package).
The dataset covers **`r nrow(dfstudy1)`** occupations measured across Canada.
The mean prestige score is **`r round(mean(dfstudy1$prestige_cont), 1)`**
(SD = `r round(sd(dfstudy1$prestige_cont), 1)`),
with values ranging from `r min(dfstudy1$prestige_cont)` to `r max(dfstudy1$prestige_cont)`.

We examine how income, education, gender composition, and occupational type predict prestige.

## Data and Variables

### Descriptive Statistics

@tbl-descriptives reports summary statistics for all processed variables.

```{r}
#| label: tbl-descriptives
#| tbl-cap: "Descriptive statistics of processed variables"

vtable::st(
  dfstudy1,
  labels         = TRUE,
  out            = "kable",
  summ           = c("notNA(x)", "mean(x)", "median(x)", "sd(x)", "min(x)", "max(x)"),
  summ.names     = c("N", "Mean", "Median", "SD", "Min", "Max"),
  factor.numeric = FALSE,
  digits         = 2,
  title          = ""
) %>%
  kable_styling(
    latex_options = c("striped", "hold_position", "scale_down"),
    full_width    = FALSE,
    font_size     = 9
  ) %>%
  footnote(general = "Numeric variables: mean, median, SD, min, max. Categorical: counts and percentages.",
           footnote_as_chunk = TRUE)
```

## Visualizations

### Univariate Distributions

@fig-hist shows the distribution of prestige scores across occupations.
The distribution is roughly symmetric with a slight right skew.
@fig-bar displays the frequency of income categories.

```{r}
#| label: fig-hist
#| fig-cap: "Distribution of occupational prestige scores"
#| fig-width: 6
#| fig-height: 3.5
#| fig-align: center

ggplot(dfstudy1, aes(x = prestige_cont)) +
  geom_histogram(bins = 15, fill = "steelblue", alpha = 0.7) +
  labs(x = "Prestige Score", y = "Frequency") +
  theme_minimal()
```

```{r}
#| label: fig-bar
#| fig-cap: "Frequency of income categories"
#| fig-width: 6
#| fig-height: 3.5
#| fig-align: center

ggplot(dfstudy1, aes(x = income_cat, fill = income_cat)) +
  geom_bar(show.legend = FALSE) +
  labs(x = "Income Category", y = "Count") +
  theme_minimal()
```

### Bivariate Relationships

@fig-scatter-edu presents the relationship between education and prestige, and
@fig-scatter-box shows the distribution of prestige across income categories.
Both panels suggest that higher education and income are associated with greater occupational prestige.

```{r}
#| label: fig-scatter-edu
#| fig-cap: "Prestige vs. years of education"
#| fig-width: 6
#| fig-height: 3.5
#| fig-align: center

ggplot(dfstudy1, aes(x = education_cont, y = prestige_cont)) +
  geom_point(alpha = 0.6, size = 2, color = "steelblue") +
  geom_smooth(method = "lm", se = TRUE, color = "red") +
  labs(x = "Years of Education", y = "Prestige Score") +
  theme_minimal()
```

```{r}
#| label: fig-scatter-box
#| fig-cap: "Prestige score by income category"
#| fig-width: 6
#| fig-height: 3.5
#| fig-align: center

ggplot(dfstudy1, aes(x = income_cat, y = prestige_cont, fill = income_cat)) +
  geom_boxplot(alpha = 0.7, show.legend = FALSE) +
  geom_jitter(width = 0.2, alpha = 0.3) +
  labs(x = "Income Category", y = "Prestige Score") +
  theme_minimal()
```

## Regression Analysis

We estimate four OLS models predicting occupational prestige.
Models 1 and 2 use continuous predictors; Models 3 and 4 use categorical versions.
The full model (Model 4) explains
**`r scales::percent(summary(model_4)$r.squared, accuracy = 0.1)`** of the variance in prestige
and includes gender composition and blue-collar status as additional controls.

Results are reported in @tbl-regression.

```{r}
#| label: tbl-regression
#| tbl-cap: "OLS regression models predicting occupational prestige"
#| results: asis

coef_map <- list(
  "(Intercept)"          = "Intercept",
  "income_cont"          = "Income (continuous)",
  "education_cont"       = "Education (continuous)",
  "income_catMid"        = "Income: Mid (ref. Low)",
  "income_catHigh"       = "Income: High (ref. Low)",
  "education_levelMid"   = "Education: Mid (ref. Low)",
  "education_levelHigh"  = "Education: High (ref. Low)",
  "women_pct"            = "Women (\\%)",
  "high_womenYes"        = "High women share: Yes (ref. No)",
  "blue_collarYes"       = "Blue collar: Yes (ref. No)"
)

texreg(
  list(model_1, model_2, model_3, model_4),
  custom.coef.map    = coef_map,
  custom.model.names = c("M1 Cont.", "M2 Cont.", "M3 Cat.", "M4 Cat."),
#  caption            = "OLS regression models predicting occupational prestige",
  caption.above      = TRUE,
  booktabs           = TRUE,
  use.packages       = FALSE
)
```

## Conclusion

Using the `Prestige` dataset (`r nrow(dfstudy1)` occupations), we find that both income and education
are strong positive predictors of occupational prestige.
The best-fitting model (M4) achieves an adjusted R² of
`r round(summary(model_4)$adj.r.squared, 3)`,
confirming that categorical indicators alongside gender composition and occupational type
explain most of the variance in prestige scores.
