---
bibliography: "bib/phd-tesis.bib" 
---

```{r, include=FALSE}
knitr::opts_chunk$set(fig.retina = 2, dpi = 300)
```

# IPO Protocol in R {background-color=#CC003D}

## Creating an RProject

### In RStudio:

1. **File** → **New Project**
2. Choose **New Directory** 
3. Select **New Project**
4. Enter project name (e.g., `bigsss-study`)
5. Choose parent directory
6. Click **Create Project**

### Result:
- `.Rproj` file created in project root
- New RStudio session opens with correct working directory
- `here::here()` will work reliably across all subdirectories

## Project Structure

::: {style="font-size: 1.5em;"}
```
project/
├── input/
│   ├── original/
│   │   └── data_original.dta
│   └── data/
│       └── proc/
│           ├── dfstudy1.RData
│           └── table000.html
├── processing/
│   └── prod_processing.R 
├── output/
│   ├── images/
│   └── tables/
└── README.md
└── main_document.qmd
└── bigsss-study.Rproj
```
:::

## Packages I like

- **Support / workflow**
  - `here` (project-safe file paths)
  - `pacman` (package loading/installation)

- **Data manipulation**
  - `dplyr` (data wrangling)
  - `car` (datasets and recoding)

- **Data reporting**
  - `kableExtra` (publication-style tables)
  - `broom` (tidy model outputs)
  - `texreg` (regression tables)
  - `sjPlot` (codebooks)
  - `vtable` (full descriptive tables)
  - `ggplot2` (figures and visual reporting)


## Installing and loading packages with pacman {auto-animate=true}

**Step 1:** Install `pacman` if not already available

```{r, eval=FALSE, echo=TRUE}
if (!requireNamespace("pacman", quietly = TRUE))
  install.packages("pacman", repos = "https://cloud.r-project.org")
```

## Installing and loading packages with pacman {auto-animate=true}

**Step 2:** Add support / workflow packages

```{r, eval=FALSE, echo=TRUE}
if (!requireNamespace("pacman", quietly = TRUE))
  install.packages("pacman", repos = "https://cloud.r-project.org")

pacman::p_load(
  # Support / workflow
  pacman, here
)
```

## Installing and loading packages with pacman {auto-animate=true}

**Step 3:** Add data manipulation packages

```{r, eval=FALSE, echo=TRUE}
if (!requireNamespace("pacman", quietly = TRUE))
  install.packages("pacman", repos = "https://cloud.r-project.org")

pacman::p_load(
  # Support / workflow
  pacman, here,
  # Data manipulation
  dplyr, car
)
```

## Installing and loading packages with pacman {auto-animate=true}

**Step 4:** Add all reporting packages — ready to run!

```{r, eval=TRUE, echo=TRUE}
if (!requireNamespace("pacman", quietly = TRUE))
  install.packages("pacman", repos = "https://cloud.r-project.org")

pacman::p_load(
  # Support / workflow
  pacman, here,
  # Data manipulation
  dplyr, car,
  # Data reporting
  kableExtra, broom, texreg, sjPlot, vtable, ggplot2
)
```

## Example: Data Processing Script {auto-animate=true}

Load libraries and use the `Prestige` dataset from the `car` package:

```{r, eval=FALSE, echo=TRUE}
rm(list = ls())
if (!requireNamespace("pacman", quietly = TRUE)) install.packages("pacman", repos = "https://cloud.r-project.org")
pacman::p_load(here, car, dplyr)
data(Prestige)
data_orig <- Prestige
```

## Example: Data Processing Script {auto-animate=true}

Load libraries and use the `Prestige` dataset from the `car` package:

```{r, eval=TRUE, echo=TRUE}
rm(list = ls())
if (!requireNamespace("pacman", quietly = TRUE)) install.packages("pacman", repos = "https://cloud.r-project.org")
pacman::p_load(here, car, dplyr)
data(Prestige)
data_orig <- Prestige
str(data_orig)  # inspect raw data structure
```

## Recode Variables from Prestige {auto-animate=true}

Create categorical, dummy, and continuous variables:

```{r, eval=FALSE, echo=TRUE}
dfstudy1 <- data_orig %>%
  mutate(
    prestige_cont = prestige,
    income_cont = income,
    education_cont = education,
    women_pct = women
  ) %>%
  as.data.frame()
```

## Recode Variables from Prestige {auto-animate=true}

Create categorical, dummy, and continuous variables:

```{r, eval=FALSE, echo=TRUE}
dfstudy1 <- data_orig %>%
  mutate(
    prestige_cont = prestige,
    income_cont = income,
    education_cont = education,
    women_pct = women,
    income_cat = car::recode(income, 
      "1000:8000 = 'Low'; 8001:12000 = 'Mid'; else = 'High'"),
    education_level = car::recode(education,
      "lo:10.09 = 'Low'; 10.1:13 = 'Mid'; 13.1:hi = 'High'"),
    prestige_tier = car::recode(prestige,
      "0:30.5 = 'Low'; 30.6:60 = 'Mid'; 60.1:100 = 'High'"),
    blue_collar = car::recode(type, "'bc' = 1; else = 0"),
    professional = car::recode(type, "'prof' = 1; else = 0"),
    high_women = car::recode(women, "50:100 = 1; else = 0")
  ) %>%
  as.data.frame()
```

## Recode Variables from Prestige {auto-animate=true}

Create categorical, dummy, and continuous variables:

```{r, eval=TRUE, echo=TRUE}
dfstudy1 <- data_orig %>%
  mutate(
    prestige_cont = prestige,
    income_cont = income,
    education_cont = education,
    women_pct = women,
    income_cat = car::recode(income, 
      "1000:8000 = 'Low'; 8001:12000 = 'Mid'; else = 'High'"),
    education_level = car::recode(education,
      "lo:10.09 = 'Low'; 10.1:13 = 'Mid'; 13.1:hi = 'High'"),
    prestige_tier = car::recode(prestige,
      "0:30.5 = 'Low'; 30.6:60 = 'Mid'; 60.1:100 = 'High'"),
    blue_collar = car::recode(type, "'bc' = 1; else = 0"),
    professional = car::recode(type, "'prof' = 1; else = 0"),
    high_women = car::recode(women, "50:100 = 1; else = 0")
  ) %>%
  as.data.frame()
# create directories and save
dir.create(here("input/data/proc"), recursive = TRUE, showWarnings = FALSE)
dir.create(here("output/images"), recursive = TRUE, showWarnings = FALSE)
dir.create(here("output/tables"), recursive = TRUE, showWarnings = FALSE)
save(dfstudy1, file = here("input/data/proc/dfstudy1.RData"))
str(dfstudy1)
```

## Codebook (HTML) with sjPlot {auto-animate=true}

```{r, eval=FALSE, echo=TRUE}
#| results: 'hide'
pacman::p_load(sjPlot)
```

## Codebook (HTML) with sjPlot {auto-animate=true}

```{r, eval=TRUE, echo=TRUE}
#| results: 'hide'
pacman::p_load(sjPlot)
sjPlot::view_df(dfstudy1, file = here("input/data/proc/table000.html")) # save codebook as HTML
```

<div style="transform: scale(0.55); transform-origin: top left; width: 182%; max-height: 70vh; overflow-y: auto;">

```{r, eval=TRUE, echo=FALSE}
load(here("input/data/proc/dfstudy1.RData"))  
pacman::p_load(sjPlot)
sjPlot::view_df(dfstudy1)
```

</div>

## Full Descriptive Table with st() (Code) {auto-animate=true}

```{r, eval=FALSE, echo=TRUE}
#| results: 'hide'
pacman::p_load(vtable, kableExtra)
sumtable_plain <- vtable::st(
  dfstudy1,
  summ = c("notNA(x)", "mean(x)", "median(x)", "sd(x)", "min(x)", "max(x)"),
  summ.names = c("N", "Mean", "Median", "SD", "Min", "Max"),
  factor.numeric = FALSE,
  digits = 2,
  out = "return",
  title = "Table 001. Full descriptive table of processed variables"
)
capture.output(print(sumtable_plain), file = here("output/tables/table001.txt"))
```

## Full Descriptive Table with st() (Code) {auto-animate=true}

```{r, eval=TRUE, echo=TRUE}
#| results: 'hide'
pacman::p_load(vtable, kableExtra)
sumtable_plain <- vtable::st(
  dfstudy1,
  summ = c("notNA(x)", "mean(x)", "median(x)", "sd(x)", "min(x)", "max(x)"),
  summ.names = c("N", "Mean", "Median", "SD", "Min", "Max"),
  factor.numeric = FALSE,
  digits = 2,
  out = "return",
  title = "Table 001. Full descriptive table of processed variables"
)
capture.output(print(sumtable_plain), file = here("output/tables/table001.txt"))

tab001 <- vtable::st(
  dfstudy1,
  labels = TRUE,
  out = "kable",
  summ = c("notNA(x)", "mean(x)", "median(x)", "sd(x)", "min(x)", "max(x)"),
  summ.names = c("N", "Mean (%)", "Median", "SD", "Min", "Max"),
  factor.numeric = FALSE,
  digits = 2,
  title = "Table 001. Full descriptive table of processed variables"
) %>%
  kable_classic(html_font = "sans", full_width = FALSE) %>%
  footnote(general = "Numeric variables report mean, median, SD, min, and max. Categorical variables report counts and percentages.")
kableExtra::save_kable(tab001, here("output/tables/table001.html"))
```

## Full Descriptive Table with st() (Output: plain text)

```{r, eval=TRUE, echo=FALSE}
txt_sumtable <- paste(readLines(here("output/tables/table001.txt")), collapse = "\n")
cat(txt_sumtable)
```

## Full Descriptive Table with st() (Output: HTML)

<div style="transform: scale(0.58); transform-origin: top left; width: 172%; max-height: 70vh; overflow-y: auto;">

```{r, eval=TRUE, echo=FALSE}
tab001
```

</div>

## Univariate Visualizations (Code) {auto-animate=true}

```{r, eval=FALSE, echo=TRUE}
#| results: 'hide'
#| fig-show: 'hide'
library(ggplot2)
load(here("input/data/proc/dfstudy1.RData"))
p_hist <- ggplot(dfstudy1, aes(x = prestige_cont)) +
  geom_histogram(bins = 15, fill = "steelblue", alpha = 0.7) +
  labs(title = "Figure 001. Distribution of Prestige Score", x = "Prestige", y = "Frequency") +
  theme_minimal()
ggsave(here("output/images/figure001.png"), p_hist, width = 8, height = 5, dpi = 600)
```

## Univariate Visualizations (Code) {auto-animate=true}

```{r, eval=TRUE, echo=TRUE}
#| results: 'hide'
#| fig-show: 'hide'
library(ggplot2)
load(here("input/data/proc/dfstudy1.RData"))
p_hist <- ggplot(dfstudy1, aes(x = prestige_cont)) +
  geom_histogram(bins = 15, fill = "steelblue", alpha = 0.7) +
  labs(title = "Figure 001. Distribution of Prestige Score", x = "Prestige", y = "Frequency") +
  theme_minimal()
ggsave(here("output/images/figure001.png"), p_hist, width = 8, height = 5, dpi = 600)
p_bar <- ggplot(dfstudy1, aes(x = income_cat, fill = income_cat)) +
  geom_bar(show.legend = FALSE) +
  labs(title = "Figure 002. Distribution of Income Categories", x = "Income Category", y = "Count") +
  theme_minimal()
ggsave(here("output/images/figure002.png"), p_bar, width = 8, height = 5, dpi = 600)
```

## Univariate Visualizations (Output)

```{r, eval=TRUE, echo=TRUE}
#| include: true
#| layout-ncol: 2
#| width: 100%
#| height: 100%
#| fig-align: center
#| fig-cap: "Figures 001-002. Univariate visualizations" 
p_hist
p_bar 
```

## Bivariate Visualizations (Code) {auto-animate=true}

```{r, eval=FALSE, echo=TRUE}
#| results: 'hide'
#| fig-show: 'hide'
p_box <- ggplot(dfstudy1, aes(x = income_cat, y = prestige_cont, fill = income_cat)) +
  geom_boxplot(alpha = 0.7, show.legend = FALSE) +
  geom_jitter(width = 0.2, alpha = 0.3) +
  labs(title = "Figure 003. Prestige Score by Income Category", x = "Income Category", y = "Prestige Score") +
  theme_minimal()
ggsave(here("output/images/figure003.png"), p_box, width = 8, height = 5, dpi = 600)
```

## Bivariate Visualizations (Code) {auto-animate=true}

```{r, eval=TRUE, echo=TRUE}
#| results: 'hide'
#| fig-show: 'hide'
p_box <- ggplot(dfstudy1, aes(x = income_cat, y = prestige_cont, fill = income_cat)) +
  geom_boxplot(alpha = 0.7, show.legend = FALSE) +
  geom_jitter(width = 0.2, alpha = 0.3) +
  labs(title = "Figure 003. Prestige Score by Income Category", x = "Income Category", y = "Prestige Score") +
  theme_minimal()
ggsave(here("output/images/figure003.png"), p_box, width = 8, height = 5, dpi = 600)
p_scatter <- ggplot(dfstudy1, aes(x = education_cont, y = prestige_cont)) +
  geom_point(alpha = 0.6, size = 3, color = "steelblue") +
  geom_smooth(method = "lm", se = TRUE, color = "red") +
  labs(title = "Figure 004. Prestige vs Education", x = "Years of Education", y = "Prestige Score") +
  theme_minimal()
ggsave(here("output/images/figure004.png"), p_scatter, width = 8, height = 5, dpi = 600)
```

## Bivariate Visualizations (Output)

```{r, eval=TRUE, echo=TRUE}
#| layout-ncol: 2
p_box
p_scatter
```

## Regression Analysis (Code) {auto-animate=true}

Model prestige as a function of income, education, women %, and blue collar status:

```{r, eval=FALSE, echo=TRUE}
#| results: 'hide'
pacman::p_load(broom, texreg)
df_reg <- dfstudy1 %>%
  mutate(
    income_cat = factor(income_cat, levels = c("Low", "Mid", "High")),
    education_level = factor(education_level, levels = c("Low", "Mid", "High")),
    high_women = factor(high_women, levels = c(0, 1), labels = c("No", "Yes")),
    blue_collar = factor(blue_collar, levels = c(0, 1), labels = c("No", "Yes"))
  )
```

## Regression Analysis (Code) {auto-animate=true}

Model prestige as a function of income, education, women %, and blue collar status:

```{r, eval=FALSE, echo=TRUE}
#| results: 'hide'
pacman::p_load(broom, texreg)
df_reg <- dfstudy1 %>%
  mutate(
    income_cat = factor(income_cat, levels = c("Low", "Mid", "High")),
    education_level = factor(education_level, levels = c("Low", "Mid", "High")),
    high_women = factor(high_women, levels = c(0, 1), labels = c("No", "Yes")),
    blue_collar = factor(blue_collar, levels = c(0, 1), labels = c("No", "Yes"))
  )
model_1 <- lm(prestige_cont ~ income_cont + education_cont, data = df_reg)
model_2 <- lm(prestige_cont ~ income_cont + education_cont + women_pct + blue_collar, data = df_reg)
model_3 <- lm(prestige_cont ~ income_cat + education_level, data = df_reg)
model_4 <- lm(prestige_cont ~ income_cat + education_level + high_women + blue_collar, data = df_reg)
model <- model_4
model_summary <- summary(model)
```

## Regression Analysis (Code) {auto-animate=true}

Model prestige as a function of income, education, women %, and blue collar status:

```{r, eval=TRUE, echo=TRUE}
#| results: 'hide'
pacman::p_load(broom, texreg)
df_reg <- dfstudy1 %>%
  mutate(
    income_cat = factor(income_cat, levels = c("Low", "Mid", "High")),
    education_level = factor(education_level, levels = c("Low", "Mid", "High")),
    high_women = factor(high_women, levels = c(0, 1), labels = c("No", "Yes")),
    blue_collar = factor(blue_collar, levels = c(0, 1), labels = c("No", "Yes"))
  )
model_1 <- lm(prestige_cont ~ income_cont + education_cont, data = df_reg)
model_2 <- lm(prestige_cont ~ income_cont + education_cont + women_pct + blue_collar, data = df_reg)
model_3 <- lm(prestige_cont ~ income_cat + education_level, data = df_reg)
model_4 <- lm(prestige_cont ~ income_cat + education_level + high_women + blue_collar, data = df_reg)
model <- model_4
model_summary <- summary(model)
# Compare model fit statistics across all 4 models
compare_models <- bind_rows(
  glance(model_1) %>% mutate(model = "Continuous M1"),
  glance(model_2) %>% mutate(model = "Continuous M2"),
  glance(model_3) %>% mutate(model = "Categorical M3"),
  glance(model_4) %>% mutate(model = "Categorical M4")
) %>%
  select(model, nobs, r.squared, adj.r.squared, sigma, AIC, BIC)
```

## Regression Analysis (Output)

```{r, eval=TRUE, echo=TRUE}
model_summary # Summary of the final model
compare_models # Comparison of model fit statistics across all 4 models
```

# texreg for regression tables

## Regression Table with screenreg (Code) {auto-animate=true}

```{r, eval=FALSE, echo=TRUE}
#| results: 'hide'
pacman::p_load(texreg)
coef_map <- list(
  "(Intercept)" = "Intercept",
  "income_cont" = "Income (continuous)",
  "income_catMid" = "Income: Mid (ref. Low)",
  "income_catHigh" = "Income: High (ref. Low)",
  "education_levelMid" = "Education: Mid (ref. Low)",
  "education_levelHigh" = "Education: High (ref. Low)",
  "high_womenYes" = "High women share: Yes (ref. No)",
  "blue_collarYes" = "Blue collar: Yes (ref. No)"
)
```

## Regression Table with screenreg (Code) {auto-animate=true}

```{r, eval=TRUE, echo=TRUE}
#| results: 'hide'
pacman::p_load(texreg)
coef_map <- list(
  "(Intercept)" = "Intercept",
  "income_cont" = "Income (continuous)",
  "income_catMid" = "Income: Mid (ref. Low)",
  "income_catHigh" = "Income: High (ref. Low)",
  "education_levelMid" = "Education: Mid (ref. Low)",
  "education_levelHigh" = "Education: High (ref. Low)",
  "high_womenYes" = "High women share: Yes (ref. No)",
  "blue_collarYes" = "Blue collar: Yes (ref. No)"
)
screenreg(list(model_1, model_2, model_3, model_4),
          file = here("output/tables/table002.txt"),
          caption = "Table 002. Comparison of continuous and categorical model specifications (4 models)",
          custom.coef.map = coef_map,
          custom.header = list("Continuous" = 1:2, "Categorical" = 3:4),
          custom.note = "%stars. Data source: `Prestige` dataset from the `car` package.")
```

## Regression Table with screenreg (Output)

```{r, eval=TRUE, echo=FALSE}
txt_reg <- paste(readLines(here("output/tables/table002.txt")), collapse = "\n")
cat(txt_reg)
```

## Regression Table with htmlreg (Code) {auto-animate=true}

```{r, eval=FALSE, echo=TRUE}
#| results: 'hide'
pacman::p_load(texreg)
htmlreg(list(model_1, model_2, model_3, model_4),
    file = here("output/tables/table002.html"),
  caption = "Table 002. Comparison of continuous and categorical model specifications (4 models)",
        caption.above = TRUE,
  custom.coef.map = coef_map
)
```

## Regression Table with htmlreg (Code) {auto-animate=true}

```{r, eval=TRUE, echo=TRUE}
#| results: 'hide'
pacman::p_load(texreg)
htmlreg(list(model_1, model_2, model_3, model_4),
    file = here("output/tables/table002.html"),
  caption = "Table 002. Comparison of continuous and categorical model specifications (4 models)",
        caption.above = TRUE,
  custom.coef.map = coef_map,
  custom.header = list("Continuous" = 1:2, 
                        "Categorical" = 3:4),
  custom.note = "%stars. Data source: `Prestige` dataset from the `car` package.")
```

## Regression Table with htmlreg (Output)

<div style="max-height:none; overflow:visible; transform: scale(0.58); transform-origin: top left; width: 172%;">

```{r, eval=TRUE, echo=FALSE}
htmltools::includeHTML(here("output/tables/table002.html"))
```

</div>

# kableExtra for tables

## kableExtra table by occupation (Code) {auto-animate=true}

```{r, eval=FALSE, echo=TRUE}
#| label: example-kableextra
#| results: 'hide'
pacman::p_load(kableExtra)
tab_occ <- dfstudy1 %>%
  group_by(type) %>%
  summarise(
    mean_income = mean(income_cont, na.rm = TRUE),
    mean_education = mean(education_cont, na.rm = TRUE),
    .groups = "drop"
  )
```

## kableExtra table by occupation (Code) {auto-animate=true}

```{r, eval=TRUE, echo=TRUE}
#| label: example-kableextra2
#| results: 'hide'
pacman::p_load(kableExtra)
tab_occ <- dfstudy1 %>%
  group_by(type) %>%
  summarise(
    mean_income = mean(income_cont, na.rm = TRUE),
    mean_education = mean(education_cont, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(type = dplyr::case_when(
    type == "bc" ~ "Blue collar",
    type == "prof" ~ "Professional",
    type == "wc" ~ "white collar",
    is.na(type) ~ "Missing",
    TRUE ~ "Other"
  )) %>%
  arrange(match(type, c("Blue collar", "Professional", 
                        "white collar", "Missing", "Other"))) %>%
  mutate(occupation_group = if_else(type == "Blue collar", "Manual", "Non-manual")) %>%
  mutate(across(c(mean_income, mean_education), ~ round(.x, 2)))
```

## kableExtra table by occupation (Output: raw summary)

```{r, eval=TRUE, echo=TRUE}
tab_occ
```

## kableExtra styled tables (Code) {auto-animate=true}

```{r, eval=FALSE, echo=TRUE}
#| label: example-kableextra-styled
#| results: 'hide'
tab_occ_html <- tab_occ %>%
  select(type, mean_income, mean_education) %>%
  kbl(
    col.names = c("Occupation type", "Average income", "Average education"),
    caption = "Table 003. Average income and education by occupation type (striped)",
    align = c("l", "r", "r")
  ) %>%
  kable_styling(full_width = FALSE, font_size = 16, bootstrap_options = c("striped", "condensed")) %>%
  column_spec(1:3, extra_css = "font-family: sans-serif;") %>%
  add_header_above(c(" " = 1, "Averages by occupation type" = 2)) %>%
  group_rows("Manual occupation", 1, 1) %>%
  group_rows("Non-manual occupations", 2, 3) %>%
  footnote(general = "Means are computed from the Prestige data (car package).", 
           number = "Income is measured in dollars; education in years.")
save_kable(tab_occ_html, file = here("output/tables/table003.html"))
```

## kableExtra styled tables (Code) {auto-animate=true}

```{r, eval=TRUE, echo=TRUE}
#| label: example-kableextra-styled2
#| results: 'hide'
tab_occ_html <- tab_occ %>%
  select(type, mean_income, mean_education) %>%
  kbl(
    col.names = c("Occupation type", "Average income", "Average education"),
    caption = "Table 003. Average income and education by occupation type (striped)",
    align = c("l", "r", "r")
  ) %>%
  kable_styling(full_width = FALSE, font_size = 16, bootstrap_options = c("striped", "condensed")) %>%
  column_spec(1:3, extra_css = "font-family: sans-serif;") %>%
  add_header_above(c(" " = 1, "Averages by occupation type" = 2)) %>%
  group_rows("Manual occupation", 1, 1) %>%
  group_rows("Non-manual occupations", 2, 3) %>%
  footnote(general = "Means are computed from the Prestige data (car package).", 
           number = "Income is measured in dollars; education in years.")
save_kable(tab_occ_html, file = here("output/tables/table003.html"))

tab_occ_classic <- tab_occ %>%
  select(type, mean_income, mean_education) %>%
  kbl(
    col.names = c("Occupation type", "Average income", "Average education"),
    caption = "Table 004. Average income and education by occupation type (kable_classic)",
    align = c("l", "r", "r")
  ) %>%
  kable_classic(full_width = FALSE, html_font = "sans") %>%
  kable_styling(full_width = FALSE, font_size = 16) %>%
  add_header_above(c(" " = 1, "Averages by occupation type" = 2)) %>%
  group_rows("Manual occupation", 1, 1) %>%
  group_rows("Non-manual occupations", 2, 3) %>%
  footnote(general = "Classic style with grouped rows.", 
          number = "Categories: Blue collar, Professional, white collar.")
save_kable(tab_occ_classic, file = here("output/tables/table004.html"))
```

## kableExtra table by occupation (Output: Striped)

```{r, eval=TRUE, echo=TRUE}
tab_occ_html
```

## kableExtra table by occupation (Output: kable_classic)

```{r, eval=TRUE, echo=TRUE}
tab_occ_classic
```

# Let put all together {background-color=#CC003D}

